Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
examples of complex nominals
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60873 72bbbca6-d526-0410-a7d9-f06f51895060

@@

%%%%% Stuff for this paper %%%%%
\usepackage{tikz-dependency}
\newcommand{\gmk}[1]{\texttt{#1}}
\newcommand{\tag}[1]{\texttt{‹#1›}}
\newcommand{\udtag}[1]{\texttt{@#1}}
\newcommand{\udlabel}[1]{{\udfont #1}}
%\newcommand{\corrauthor}[1]{\footnotemark\footnotetext{hargle}}

@@

\begin{figure}[htbp]
	\centering
	\begin{dependency}[theme = simple, font = \small]
	   \begin{deptext}[column sep=0.3cm]
			әлем \& чемпионаты \\
			\gmk{n.nom} \& \gmk{n.px3sg.nom} \\
		\end{deptext}
		\depedge{1}{2}{\udlabel{nmod}}
	\end{dependency}
	\caption{A nominal depending on an indefinite genitive.}\label{fig:indefgen}
\end{figure}

>>>>

\usepackage{subcaption}

@@

%%%%% Stuff for this paper %%%%%
\usepackage{tikz-dependency}
\newcommand{\gmk}[1]{\texttt{#1}}
\newcommand{\gloss}[1]{#1}
\newcommand{\tag}[1]{\texttt{‹#1›}}
\newcommand{\udtag}[1]{\texttt{@#1}}
\newcommand{\udlabel}[1]{{\udfont #1}}
%\newcommand{\corrauthor}[1]{\footnotemark\footnotetext{hargle}}

@@

\begin{figure}[htbp]
	\centering

	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				көрші \& елдер \\
				\gmk{n.attr} \& \gmk{n.pl.nom} \\
				\gloss{neighbour} \& \gloss{countries} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{compound}}
		\end{dependency}
		\caption{Compounding: a nominal depending on an attributive nominal.}\label{fig:compound}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				әлем \& чемпионаты \\
				\gmk{n.nom} \& \gmk{n.px3sg.nom} \\
				\gloss{world} \& \gloss{championship} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Indefinite genitive: A nominal depending on an indefinite genitive.}\label{fig:indefgen}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				Иранның \& экономиясы \\
				\gmk{n.gen} \& \gmk{n.px3sg.nom} \\
				\gloss{Iran's} \& \gloss{economy} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Definite genitive: A nominal depending on an definite genitive.}\label{fig:indefgen}
	\end{subfigure}

	\caption{Dependency trees of complex nominal relations.}
\end{figure}
